---
title: "Video Game Global Sales Analysis Project"
author: "Yucheng Feng, Boda Song, Bowen Gu"
date: "11/30/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(faraway)
library(ISLR)
library(MASS)
library(faraway)
```

## R Markdown
## Including Plots

```{r cleaning}
df_game = read.csv('video_game.csv')
df_game_new = subset(df_game, Publisher == 'Nintendo' | Publisher == 'Ubisoft' | Publisher == 'Microsoft Game Studios' | Publisher == 'Activision', select = c(Name,Global_Sales,NA_Sales,JP_Sales,Publisher,Critic_Score,User_Score))

df_game_new<-df_game_new[-which(is.na(df_game_new$Critic_Score),is.na(df_game_new$Userc_Score),is.na(df_game_new$Global_Sales)),]
df_game_clean <- filter(df_game_new, Global_Sales > 0, NA_Sales > 0, JP_Sales > 0, Critic_Score > 0,User_Score>0,User_Score != 'tbd')
head(df_game_new)
nrow(df_game_new)
```

```{r pressure, echo=FALSE}
games = read.csv('game_clean.csv')
games_data = data.frame(games)
model_1 = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + Critic_Score + User_Score, data=games_data)
summary(model_1)
```

For every 1 million increase in NA_Sales, I expect the Global_Sales to increase by 1.7349 million on average, holding JP_Sales, Publisher, Critic_Score and User_Score constant.

I expect the intercept should be 0.644479 the publisher company of game is Nintendo, holding all other slopes to be the same.

```{r model}
model_jp = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + Critic_Score + User_Score + Publisher*JP_Sales, data=games_data)
summary(model_jp)
```
Choice: JP_Sales*Publisher

```{r forward}
game_start = lm(Global_Sales ~ 1, data = games_data)
game_model_forward = step(
  game_start, 
  scope = Global_Sales ~ NA_Sales + JP_Sales + Publisher + 
    Critic_Score + User_Score + JP_Sales:Publisher, 
  direction = "forward")
```

```{r inclation}
# Use this code chunk for your answer.
model_start = lm(Global_Sales ~ NA_Sales + JP_Sales + 
    Critic_Score + User_Score, data = games_data)
vif(model_start) # previous
model_remove_category = lm(Global_Sales ~ NA_Sales + JP_Sales  + 
    Critic_Score, data = games_data)
print("/")
vif(model_remove_category) # after

```
Variance Inflation Factor tells us how much a variable is inflated due to multicollinearity in the model. Variance Inflation Factor helps us identify whether a variable is correlated with other variables in the model. 

```{r model2}
summary(model_jp)
final_model = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + 
    Critic_Score + JP_Sales:Publisher,data = games_data)
summary(final_model)
```
98.65% of the variation in the game global sales can be explained by their linear relationship with model includes NA_Sales, JP_Sales, Critic_Score, Publisher, User_Score NA_Sales:JP_Sales, JP_Sales:Publisher.

98.61% of the variation in the game global sales can be explained by their linear relationship with model includes NA_Sales, JP_Sales, Critic_Score, Publisher, NA_Sales:JP_Sales, JP_Sales:Publisher.

```{r lev}
p = 10
n = nrow(games_data)
n
2*p/n
hatvalues(final_model)[hatvalues(final_model) > 2 * p / n]
plot(final_model)
```

```{r std}
rstand = data.frame(rstand = rstandard(final_model))
rstand$rstand[abs(rstand$rstand) > 2]
which(abs(rstandard(final_model)) > 2)
```

```{r cook}
n = nrow(games_data)
cooks.distance(final_model)[cooks.distance(final_model) > 4 / n]
```


```{r boxcox}
boxcox(final_model,plotit=TRUE)
```

```{r p_test}
summary(final_model)
p = 10
n = nrow(games_data)
p*10
n
```
This is reasonable, because 10*p < n

```{r anova}
final_model = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + 
    Critic_Score + JP_Sales:Publisher,data = games_data)
no_NA_model = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + 
    Critic_Score + JP_Sales:Publisher,data = games_data)
anova(final_model,no_NA_model)

final_model = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + 
    Critic_Score + JP_Sales:Publisher,data = games_data)
no_critical_model = lm(Global_Sales ~ NA_Sales + JP_Sales + Publisher + 
    JP_Sales:Publisher,data = games_data)
anova(final_model,no_critical_model)
```